Design of a urban sound scenes corpuses with controlled acoustic properties

### 2017-04-24 articleBoston.tex
bibliography correection
title and abstract

\title{Creation of a corpus of realistic urban sound scenes with controlled acoustic properties}     %% \title est une macro, entre { } figure son premier argument
\author{
  GLOAGUEN, Jean-R\'emy\      \texttt{first1.last1@xxxxx.com}
  \and
  CAN, Arnaud\      \texttt{first2.last2@xxxxx.com}
  \and
  LAGRANGE, Mathieu\      \texttt{first1.last1@xxxxx.com}
  \and
  PETIOT, Jean-Fran\c cois\      \texttt{first1.last1@xxxxx.com}
}

@@

\section*{Abstract}
An approach is proposed to simulate a panel of urban sound mixtures from a study of recorded scenes. The aim is to succeed to compose sufficiently realistic scenes to be similar to recordings realized in cities. From a listening and recording phase, some parameters are extracted and can be used in the sound mixture simulator \textit{simScene}. The real scenes are then replicated and the realism of these are compared to the recorded scenes by a perceptive test realized on 50 people. The result prove that no particular differences can be made between the simulated and the real scenes.

@@

\bibliographystyle{unsrt}
\bibliography{../bibliographie}

>>>>

\title{Design of a urban sound scenes corpuses with controlled acoustic properties}     %% \title est une macro, entre { } figure son premier argument
\author{
  GLOAGUEN, Jean-R\'emy\      \texttt{first1.last1@xxxxx.com}
  \and
  CAN, Arnaud\      \texttt{first2.last2@xxxxx.com}
  \and
  LAGRANGE, Mathieu\      \texttt{first1.last1@xxxxx.com}
  \and
  PETIOT, Jean-Fran\c cois\      \texttt{first1.last1@xxxxx.com}
}

@@

\section*{Abstract}

Monitoring the acoustic urban environment is beneficial for improving the life of citizens. To do so, the research community in acoustics can befenit from corpora where the acoustic contribution of sources of disturbance such as road traffic is precisely known.

In this paper, a set of urban sound mixtures are simulated using an open source tool \textit{simScene}. Their caracteristics (type of sources, density of events, etc.) are infered from the listening of reference audio scenes recorded in Paris, France. The main advantage of the simulated versions is that several quantities, such as the acoustic level of each source is precisely known, a useful feature for evaluated automated analysis tools.

In order to quantifiy the level of realism achieved by the use of the simulation tool a perceptive test is conducted with 50 subjects. The result show that no significative differences can be made between the simulated and the recorded scenes.

@@

\bibliographystyle{unsrt}
\bibliography{bibliography}
